---
title: "NGS PROJECT"
output: html_document
date: "2026-04-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load packages

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(DESeq2)
library(tidyverse)
library(readxl)
library(edgeR)
library(clusterProfiler)
```

#load the data 
```{r}
rdsobj <- readRDS("/opt/omicsdata/datasets/SRP045534.rds") 
rdsobj
class(rdsobj)
```
```{r}
## To visualize the raw count matrix
assays(rdsobj)
countmatrix <- rdsobj@assays@data$raw_counts
dim(countmatrix)
head(countmatrix)

```

```{r}
#we visualise first six genes and first six samples
assay(rdsobj, "raw_counts")[1:6, 1:6]
```
```{r}
colnames(rdsobj)[1:10]
```

```{r}
class(colData(rdsobj))
colData(rdsobj)[1:6, 1:10]
```
```{r}
coldata <- rdsobj@colData %>% data.frame()
coldata
```

```{r}
colnames(coldata)
```




#extract the $sra.sample_attributes
```{r}
colData(rdsobj)$sra.sample_attributes
```
```{r}
colData(rdsobj)$sra.sample_title
```

```{r}
#turn the sample title text into clean experimental variables: cell type, stage, and replicate
coldata$cell_type <- ifelse(grepl("Basal", coldata$sra.sample_title), "Basal",
                     ifelse(grepl("Luminal", coldata$sra.sample_title), "Luminal", NA))

coldata$stage <- ifelse(grepl("virgin", coldata$sra.sample_title), "virgin",
                 ifelse(grepl("18.5", coldata$sra.sample_title), "pregnant",
                 ifelse(grepl("2 dL", coldata$sra.sample_title), "lactation", NA)))

coldata$replicate <- ifelse(grepl("#1", coldata$sra.sample_title), "1",
                     ifelse(grepl("#2", coldata$sra.sample_title), "2", NA))

table(coldata$cell_type, coldata$stage)
table(coldata$replicate)
```



```{r}
sample_info <- as.data.frame(colData(rdsobj))
unique(sample_info$sra.sample_attributes)
```
```{r}
#get how many luminal and basal samples we have 

sample_info$cell_type <- ifelse(grepl("Basal", sample_info$sra.sample_title, ignore.case = TRUE), "Basal",
                         ifelse(grepl("Luminal", sample_info$sra.sample_title, ignore.case = TRUE), "Luminal", NA))

sample_info$stage <- ifelse(grepl("virgin", sample_info$sra.sample_title, ignore.case = TRUE), "virgin",
                     ifelse(grepl("18.5", sample_info$sra.sample_title, ignore.case = TRUE), "pregnant",
                     ifelse(grepl("2 dL", sample_info$sra.sample_title, ignore.case = TRUE), "lactation", NA)))

sample_info$replicate <- ifelse(grepl("#1", sample_info$sra.sample_title), "1",
                         ifelse(grepl("#2", sample_info$sra.sample_title), "2", NA))

table(sample_info$cell_type)
table(sample_info$stage)
table(sample_info$cell_type, sample_info$stage)
table(sample_info$replicate)
```

```{r}
#check the raw count matrix

counts <- assay(rdsobj, "raw_counts")
dim(counts)
counts[1:6, 1:6]
summary(counts)
```


```{r}
# Check library sizes per sample
libsizes <- colSums(counts)
libsizes
summary(libsizes)
barplot(libsizes, las = 2, main = "Library sizes", ylab = "Total counts")
```

```{r}
#group based 

sample_info$library_size <- libsizes

boxplot(library_size ~ cell_type, data = sample_info,
        main = "Library size by cell type", ylab = "Total counts")

boxplot(library_size ~ stage, data = sample_info,
        main = "Library size by stage", ylab = "Total counts")

boxplot(library_size ~ cell_type + stage, data = sample_info,
        main = "Library size by cell type and stage", ylab = "Total counts", las = 2)
```





```{r}
#Check how many zeros and low-count genes you have
sum(counts == 0)
mean(counts == 0)

gene_totals <- rowSums(counts)
summary(gene_totals)
hist(gene_totals, breaks = 50, main = "Gene total counts", xlab = "Row sums")
hist(log10(gene_totals + 1),
     breaks = 50,
     main = "Log10 gene total counts",
     xlab = "log10(row sums + 1)")
```


#The distribution of gene total counts is highly skewed, with most genes showing low total counts and a small number of genes showing very high counts. This pattern is typical of RNA-seq count data.

#The log-transformed distribution of gene total counts shows a large peak at zero, indicating many genes are not detected in any sample, while the remaining genes span a broad range of expression levels. This pattern is typical of RNA-seq data and suggests the presence of many lowly expressed genes together with a smaller number of highly expressed genes.

```{r}
#Check how many genes are expressed in how many samples
detected_samples <- rowSums(counts > 0)
table(detected_samples)
```

```{r}
#Attach the Basal/Luminal info to sample summaries

# Convert sample metadata to a regular data frame
sample_info <- as.data.frame(colData(rdsobj))
# Extract cell type from the sample title
sample_info$cell_type <- ifelse(
  grepl("Basal", sample_info$sra.sample_title, ignore.case = TRUE), "Basal",
  ifelse(grepl("Luminal", sample_info$sra.sample_title, ignore.case = TRUE), "Luminal", NA)
)
# Extract developmental stage from the sample title
sample_info$stage <- ifelse(
  grepl("virgin", sample_info$sra.sample_title, ignore.case = TRUE), "virgin",
  ifelse(grepl("18.5", sample_info$sra.sample_title, ignore.case = TRUE), "pregnant",
  ifelse(grepl("2 dL", sample_info$sra.sample_title, ignore.case = TRUE), "lactation", NA))
)
# Extract replicate number from the sample title
sample_info$replicate <- ifelse(
  grepl("#1", sample_info$sra.sample_title), "1",
  ifelse(grepl("#2", sample_info$sra.sample_title), "2", NA)
)
# Attach the library size of each sample
sample_info$library_size <- libsizes

# Display a simplified sample summary table
sample_info[, c("cell_type", "stage", "replicate", "library_size")]
```


















